Figures

### 2020-01-07 manuscript/figures.Rmd
include predictors table in figures doc
add diagrams to figures doc

>>>>

```{r 01_predictors, results='asis', warning=FALSE, echo = FALSE}
knitr::kable('\\includegraphics[width=6.5in]{"../tables/01_predictors"}', col.names = NULL, caption = "Summary of lake depth predictor variables.")
```

![Slope diagram caption](../figures/slope_diagram.pdf){width=100%}

![Lake shape caption](../figures/lake_shape.pdf){width=100%}
